Title of article

### 2025-02-06 article/main.tex
article: add experimental setup, datasets, motivation, objectives, contribution, structure

\usepackage{xcolor}
\usepackage{tcolorbox}

@@

% Script from: https://github.com/ArturB/WUT-Thesis
\RequirePackage{ifluatex}      % LuaTeX-specific options
\ifluatex
    \RequirePackage[T1]{fontenc}
    \RequirePackage[utf8]{luainputenc}
    \RequirePackage{luacode}
    % In LuaTeX, we can prevent one-letter words
    % from beging at the end of the line.
    \begin{luacode}
    local debug = false
    local glyph_id = node.id "glyph"
    local glue_id  = node.id "glue"
    local hlist_id = node.id "hlist"

@@

    % region Article Metadata
    \title{Title of article}
    \author{Patryk Filip Gryz}
    % endregion

@@

    \section{Introduction}

@@

        \subsection{Problem Statement}

            \temporary{
                Czas potrzebny do klasyfikacji taksonomicznej wielu sekwencji za pomocą klasycznych narzędzi typu BLASTn wymaga wielu godzin dla nawet relatywnie małych zbiorów sekwencji (4096)
            }

@@

            \temporary{
                Cel to przyśpieszenie klasyfikacji taksonomicznej próbki sekwencji genetycznych z środowiska poprzez klasyfikację tylko części sekwencji genetycznych.
            }

        \subsection{Contributions of the Paper}

            \temporary{
                Model sztucznej sieci neuronowej, który pozwala określać niepodobieństwo między sekwencjami, które później może zostać użyte w algorytmie grupowania, dzięki któremu możliwy jest wybór reprezentantów wykorzystywanych w klasyfikacji taksonomciznej.
            }

@@

            \temporary{
                Pierwszy rozdział zawiera wprowadzenie.
                Drugi zawiera opis powiązanych prac.
                Trzeci metodologię.
                Czwarty Eksperymenty i wyniki.
                Piąty dyskusję
                Szósty wnioski oraz dalsze kierunki rozwoju.
            }

    \section{Related Work}

@@

    \section{Methodology}

@@

    \section{Experiments and Results}

@@

            \temporary{
                Eksperymenty zostały przeprowadzone na maszynie wirtualnej wykorzystującej technologię KVM o specyfikacji podanej poniżej:

                % \subsubsection{Specyfikacja techniczna}\

                    \begin{itemize}
                        \item {
                            \textbf{System operacyjny:} Ubuntu 22.04 LTS;
                        }
                        \item {
                            \textbf{Procesor:} 4 rdzenie wirtualne procesora Intel Core i7-6850K;
                        }
                        \item {
                            \textbf{Pamięć RAM:} 40GB;
                        }
                        \item {
                            \textbf{Karta graficzna:} Nvidia GeForce GTX 1080 TI;
                        }
                        \item {
                            \textbf{Dysk:} dysk sieciowy 1 TB z prędkością odczytu 1 Gbps;
                        }
                        \item {
                            \textbf{Oprogramowanie:} pakiet \texttt{BLAST} w wersji 2.16.0 oraz sterowniki karty graficznej.
                        }
                    \end{itemize}
            }

@@

            \temporary{
                \subsubsection{Opis zbioru danych}

            W eksperymentach wykorzystano ten sam zbiór sekwencji genetycznych, co w uczeniu modelu sztucznej sieci neuronowej. Zbiór \textit{CAMI II Toy Human Microbiome Project}\cite{Fritz:2019} został wybrany, ponieważ został stworzony w celu oceny wydajności algorytmów bioinformatycznych oraz zawiera znaczną liczbę sekwencji genetycznych, co umożliwiło jego wykorzystanie go zarówno w eksperymentach, jak i w uczeniu modelu sztucznej sieci neuronowej.

            Na podstawie zbioru stworzono podzbiory sekwencji o rozmiarach wyrażonych wzorem $2^k$ dla $k \in [0, 12]$. Zbiory są rozłączne, a do ich budowy wykorzystano wyłącznie te sekwencje, które nie zostały użyte do uczenia modelu sztucznej sieci neuronowej.

        \subsubsection{Przygotowanie zbioru danych}

            Podzbiory powstały poprzez losowanie bez zwracania indeksów sekwencji genetycznych ze zbioru referencyjnego, które powinny trafić do podzbioru. W losowaniu wykorzystano informację o indeksach sekwencji wykorzystanych w zbiorze uczącym oraz walidacyjnym sztucznej sieci neuronowej. W celu umożliwienia dalszego wykorzystania zbioru danych zapisano do pliku indeksy sekwencji wykorzystanych w procesie budowy zbioru eksperymentalnego. Podzbiory sekwencji zostały zapisane do plików w formacie FASTA.
            }

@@

    \section{Discussion}

@@

    \section{Conclusions and Future Work}

>>>>

\usepackage{xcolor}
\usepackage{tcolorbox}     % Color boxes
\usepackage{amsmath}       % Basic mathematical typesetting
\usepackage{amssymb}       % Advanced math symbols
\usepackage{amsthm}        % Theorems typesetting
\usepackage{array}         % Advanced table column formats
\usepackage{enumitem}      % Itemize/enumrate
\usepackage{fancyhdr}      % Custom header/footer styles
\usepackage{fourier}       % Adobe Utopia font
\usepackage{graphicx}      % Enhanced images support
\usepackage{ifluatex}      % LuaTeX-specific options
\usepackage{kantlipsum}    % English kantian-style lipsum
\usepackage{lipsum}        % Lorem ipsum
\usepackage{listings}      % Code listings
\usepackage{longtable}     % Multi-page tables
\usepackage{multirow}      % Advanced table cells
\usepackage{setspace}      % Set space between lines
\usepackage{scrextend}     % Allows \addmargin environment
\usepackage{tablefootnote} % Table footnotes
\usepackage{tocloft}       % Custom ToC/LoF/LoT
\usepackage{url}           % URL-sensitive line breaks
\usepackage{xspace}        % Remove duplicated spaces

\setstretch{1.15}
\setlength{\parindent}{5mm}
\counterwithin{equation}{section}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

% List formatting
\setlist[itemize,1]{topsep=2pt,label=\large$\bullet$, leftmargin=28pt}
\setlist[itemize,2]{topsep=2pt,leftmargin=18pt}
\setlist[itemize,3]{topsep=2pt,leftmargin=18pt}
\setlist[enumerate,1]{topsep=2pt,leftmargin=24pt}
\setlist[enumerate,2]{topsep=2pt,leftmargin=16pt}
\setlist[enumerate,3]{topsep=2pt,leftmargin=16pt}

% List of figures
\renewcommand*\l@figure{\@dottedtocline{1}{0.5em}{2.25em}}
\newcommand{\listoffigurestoc}{
    \listoffigures
    \addcontentsline{toc}{section}{\listfigurename}
}

% List of tables
\renewcommand*\l@table{\@dottedtocline{1}{0.5em}{2.25em}}
\newcommand{\listoftablestoc}{
    \listoftables
    \addcontentsline{toc}{section}{\listtablename}
}

@@

% Script from: https://github.com/ArturB/WUT-Thesis
\usepackage{ifluatex}      % LuaTeX-specific options
\ifluatex
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{luainputenc}
    \usepackage{luacode}
    % In LuaTeX, we can prevent one-letter words
    % from beging at the end of the line.
    \begin{luacode}
    local debug = false
    local glyph_id = node.id "glyph"
    local glue_id  = node.id "glue"
    local hlist_id = node.id "hlist"

@@

    \title{Title of article}
    \author{Patryk Filip Gryz}

@@

    \clearpage
    \section{Introduction}

@@

        \subsection{Motivation}

            The time required for taxonomic classification of large sequence datasets using traditional tools, such as BLAST, can span several hours, even for relatively small collections of sequences e.g. 4096 sequences. In many fields, artificial neural networks (ANN) have demonstrated the ability to outperform classical heuristic algorithms, offering faster and more accurate results. By leveraging the capabilities of ANN, this works aims to accelerate taxonomic clasisfication process while maintaining at least the same level of quality as traditional methods.

@@

            The primary objective of this study is to leverage an artificial neural network to support the selection of representative genetic sequences for taxonomic classification. Instead of classifying entire environmental genetic sequences sample, the proposed approach focuses on identifying a subset of sequences that best represent the sample. These selected representatives are then classified, reducing computational complexity while maintaining classification accuracy.

        \subsection{Main Contributions}

            This paper introduces a novel artificial neural network model for calculating dissimilarities between genetic sequences, which can be used in clustering algorithm to select representative sequences for taxonomic classification. We provide all the necessary components for training the model, including dataset preparation, batch process, a loss function, and a training loop. The paper also includes an application that can perform taxonomic classification with specified parameters. Furthermore, we develope a library that allows users to compose the taxonomic classification pipelines.

@@

            The rest of the paper is organized as follows. Section 2 provides a description of related work, reviewing previous research on taxonomic classification and highlights a research gap. Section 3 defines the problem, presents the proposed approach, and provides detailed implementation details. Section 4 describes the experimental setup, including used datasets, the performance metrics for evaluation, and the results obtained from experiments with analysis. Section 5 interprets the results, discusses the limtiations of proposed approach, and explores possible improvements for future work. Finally, Section 6 concludes the paper by summarizing the main findings and suggesting potential directions for future research.

    \clearpage
    \section{Related Work}

@@

    \clearpage
    \section{Methodology}

@@

    \clearpage
    \section{Experiments and Results}

@@

            Experiments were conducted on the KVM based virtual machine with the specification given below:

            \begin{itemize}
                \item{
                    \textbf{Operating System:} Ubuntu 22.04 LTS;
                }
                \item{
                    \textbf{Processor:} 4 virtual cores of Intel Core i7-6850K;
                }
                \item{
                    \textbf{RAM Memory:} 40 GB;
                }
                \item{
                    \textbf{Graphics Card:} Nvidia GeForce GTX 1080 TI;
                }
                \item{
                    \textbf{Disk:} 1 TB network drive with a read speed of 1 Gbps;
                }
                \item{
                    \textbf{Software:} \texttt{BLAST} package version 2.16.0 and graphics card drivers.
                }
            \end{itemize}

@@

            \subsubsection{Dataset Description}

                In the experiments, the \textit{CAMI II Toy Human Microbiome Project}\cite{Fritz:2019} dataset was used, which is the same dataset used for training the artificial neural network model. Dataset was chosen, because it was created for benchmarking bioinformatics tools and contains a large number of sequences, enabling its use both in experiments and in the learning process.

                Subsets of sequences were created from the dataset with sizes expressed by the formula $2^k$ for $k \in [0, 12]$. Subsets are disjoint, and only those sequences that were not used for training the ANN model were employed in their construction.

            \subsubsection{Dataset Preparation}

                The subsets were created by randomly sampling, without replacement, the indices of genetic sequences from the reference dataset that were to be included in each subset. Indices of sequences used in the training and validation sets of the ANN were excluded from the sampling.

@@

    \clearpage
    \section{Discussion}

@@

    \clearpage
    \section{Conclusions and Future Work}
